Discrete Quantum Theories and Computing

### 2018-11-24 dissertation.tex
dissertation.lyx "2.2.1 Classical and Quantum Probability Spaces" Updating...

Since the probability induced by the different beam splitters are
correlated, it is more natural to define one quantum event space~$\events$
containing all possible classical event spaces using different beam
splitters. However, simply taking the union of all event spaces is
a bad idea because two events might appear different but representing
the same situation. For example, if we take the complement on the
both sides of $\mu_{0}\left(\left\{ \ket{2}\right\} \right)=\mu_{1}\left(\left\{ \ket{2}\right\} \right)$,
we will have
\begin{equation}
\mu_{0}\left(\left\{ \ket{0},\ket{1}\right\} \right)=1-\mu_{0}\left(\left\{ \ket{2}\right\} \right)=1-\mu_{1}\left(\left\{ \ket{2}\right\} \right)=\mu_{1}\left(\left\{ \ket{\ps},\ket{\ms}\right\} \right)\,,
\end{equation}
that is, the probabilities of events $\left\{ \ket{0},\ket{1}\right\} $
and $\left\{ \ket{\ps},\ket{\ms}\right\} $ are always the same, and
should be identified as the same quantum event to simplify our discussion.
Since the projectors generated by these two events are equal as operators,
i.e., $\proj{0}+\proj{1}=\proj{\ps}+\proj{\ms}$, given any classical
event~$E$, we can follow the same idea to define its quantum event
as the projector generated by $E$
\begin{equation}
\varphi\left(E\right)=\sum_{\ket{j}\in E}\proj{j}\label{eq:pullback-function}
\end{equation}
with the convention $\varphi\left(\emptyset\right)=\mathbb{0}$. This
function $\varphi$ well glues all classical event spaces into one
quantum event space~$\events$, the set of all projectors on a given
Hilbert space, because it is easy to inductively prove that if two
classical events~$E$ and $E'$ corresponding to the same quantum
event, i.e., $\varphi\left(E\right)=\varphi\left(E'\right)$, then
the probability of $E$ is the same as the probability of $E'$.

>>>>

Since the probability induced by the different beam splitters are
correlated, it is more natural to define one quantum event space~$\events$
containing all possible classical event spaces using different beam
splitters. However, simply taking the union of all event spaces is
a bad idea because two events might appear different but representing
the same situation. For example, if we take the complement on the
both sides of $\mu_{0}\left(\left\{ \ket{2}\right\} \right)=\mu_{1}\left(\left\{ \ket{2}\right\} \right)$,
we will have
\begin{equation}
\mu_{0}\left(\left\{ \ket{0},\ket{1}\right\} \right)=1-\mu_{0}\left(\left\{ \ket{2}\right\} \right)=1-\mu_{1}\left(\left\{ \ket{2}\right\} \right)=\mu_{1}\left(\left\{ \ket{\ps},\ket{\ms}\right\} \right)\,,
\end{equation}
that is, the probabilities of events $\left\{ \ket{0},\ket{1}\right\} $
and $\left\{ \ket{\ps},\ket{\ms}\right\} $ are always the same, and
these events should be identified as the same quantum event to simplify
our discussion. This can be achieved by mapping a classical event~$E$
to the projector generated by $E$
\begin{equation}
\varphi\left(E\right)=\sum_{\ket{j}\in E}\proj{j}\label{eq:pullback-function}
\end{equation}
with the convention $\varphi\left(\emptyset\right)=\mathbb{0}$ because
\begin{equation}
\varphi\left(\left\{ \ket{0},\ket{1}\right\} \right)=\proj{0}+\proj{1}=\proj{\ps}+\proj{\ms}=\varphi\left(\left\{ \ket{\ps},\ket{\ms}\right\} \right)\,.
\end{equation}
In general, if two classical events~$E$ and $E'$ mapped the same
projector, i.e., $\varphi\left(E\right)=\varphi\left(E'\right)$,
then the probability of $E$ is the same as the probability of $E'$.
the function $\varphi$ well glues all classical event spaces into
one quantum event space~$\events$.
